### 2017-10-24 Draft2/Appendix.tex
More changes

\subsection{Merging over Arithmetic Operations}
\label{pf:MergingOverArithmetic}

\begin{theorem}
	$P$ merges over addition and subtraction. That is, for functions $f$ and $g$,
	\begin{align*}
	\hat{f} \TextTilde f \land \hat{g} \TextTilde g \rightarrow \begin{cases}
	(\hat{f} + \hat{g}) \TextTilde (f + g)\\
	(\hat{f} - \hat{g}) \TextTilde (f - g)
	\end{cases}
	\end{align*}
\end{theorem}

\begin{proof}
	We will consider the statement about addition first. Recall from the note at \ref{subsec:AsymptoticProperties} that this statement is equivalent to:

@@

\begin{theorem}
	$P$ merges over multiplication and division. That is, for functions $f$ and $g$,
	\begin{align*}
	\hat{f} \TextTilde f \land \hat{g} \TextTilde g \rightarrow \begin{cases}
	\hat{f}\hat{g} \TextTilde fg\\
	\hat{f} / \hat{g} \TextTilde f / g
	\end{cases}
	\end{align*}
\end{theorem}

\begin{proof}
	We will consider the statement about multiplication first. Recall from the note at \ref{subsec:AsymptoticProperties} that this statement is equivalent to:

@@

>>>>

\subsection{Merging over Arithmetic Operations}
\label{pf:MergesOverArithmetic}

\begin{proof}[Proof (Theorem \ref{thm:MergesOverArithmeticAdd})]
	We will consider the statement about addition first. Recall from the note at \ref{subsec:AsymptoticProperties} that this statement is equivalent to:

@@

\begin{proof}[Proof (Theorem \ref{thm:MergesOverArithmeticMultiply})]
	We will consider the statement about multiplication first. Recall from the note at \ref{subsec:AsymptoticProperties} that this statement is equivalent to:

@@

\begin{theorem}
	If $f \TextTilde g$ and $g \TextTilde h$, then $f \TextTilde h$.
\end{theorem}

\begin{proof}
	By definition, $\lim_{n \to \infty} g / f = 1$ and $\lim_{n \to \infty} h / g = 1$. Multiplying the two equations, $\lim_{n \to \infty} h / f = 1$ which implies $f \TextTilde h$.
\end{proof}

### 2017-10-24 Draft2/AsymptoticNotation.tex
More changes

A useful property $\TextTilde$ shares with $O$ is that it merges over arithmetic operations. This is stated by the following two theorems, which are proved in \ref{pf:MergingOverArithmetic}.

\begin{theorem}
	$P$ merges over addition and subtraction. That is, for functions $f$ and $g$,
	\begin{align*}
	\hat{f} \TextTilde f \land \hat{g} \TextTilde g \rightarrow \begin{cases}
		(\hat{f} + \hat{g}) \TextTilde (f + g)\\
		(\hat{f} - \hat{g}) \TextTilde (f - g)
	\end{cases}
	\end{align*}
\end{theorem}

\begin{theorem}
	$P$ merges over multiplication and division. That is, for functions $f$ and $g$,
	\begin{align*}
	\hat{f} \TextTilde f \land \hat{g} \TextTilde g \rightarrow \begin{cases}
	\hat{f}\hat{g} \TextTilde fg\\
	\hat{f} / \hat{g} \TextTilde f / g
	\end{cases}
	\end{align*}
\end{theorem}

>>>>

A useful property $\TextTilde$ shares with $O$ is that it merges over arithmetic operations. This is stated by the following two theorems, which are proved in \ref{pf:MergesOverArithmetic}.

\begin{theorem}
\label{thm:MergesOverArithmeticAdd}
	$P$ merges over addition and subtraction. That is, for functions $f$ and $g$,
	\begin{align*}
	\hat{f} \TextTilde f \land \hat{g} \TextTilde g \rightarrow \begin{cases}
		(\hat{f} + \hat{g}) \TextTilde (f + g)\\
		(\hat{f} - \hat{g}) \TextTilde (f - g)
	\end{cases}
	\end{align*}
\end{theorem}

\begin{theorem}
\label{thm:MergesOverArithmeticMultiply}
	$P$ merges over multiplication and division. That is, for functions $f$ and $g$,
	\begin{align*}
	\hat{f} \TextTilde f \land \hat{g} \TextTilde g \rightarrow \begin{cases}
	\hat{f}\hat{g} \TextTilde fg\\
	\hat{f} / \hat{g} \TextTilde f / g
	\end{cases}
	\end{align*}
\end{theorem}
